18 month progress report

### 2017-03-24 reports/progress_1/progress_1.tex
In progress report, proof read.

\section{About the Data}
Data was collected prior to the mini-project. 20 black/grey/white (b/g/w) images were collected on 14/03/16 at around 1250. The b/g/w images are images obtained from the x-ray detector when exposed to x-rays at different settings. They are useful for calibrating the detector, thus b/g/w images can be called reference images. About 2 hours later, 100 images of a 3D printed cuboid (or sample) were taken. These images were obtained from the x-ray detector when exposed to x-rays with the sample between the x-ray source and detector. The 3D printed was stationary and not rotating throughout the scans. The detector used was the Perkin Elmer XRD 1621 digital x-ray detector, with settings shown in Table \ref{table:settings}.

@@

The images were $(1\,996\times1\,996)$ pixels in size and are in greyscale with 16 bits, in other words each pixel can have grey values which take integer values from 0 to $2^{16}-1$ inclusive. The grey values are in arbitrary units. The images are shown in Figure \ref{fig:image} and the histogram of grey values are shown in Figure \ref{fig:hist}.

\begin{figure*}
	\centering
	\includegraphics[width = 0.9\textwidth]{../figures/data/140316_image.eps}
	\caption{A black, grey, white and sample image obtained from the x-ray detector.}
	\label{fig:image}
\end{figure*}

\begin{figure}
	\centering
	\includegraphics[width = 0.45\textwidth]{../figures/data/140316_histo.png}
	\caption{A black, grey, white and sample image obtained from the x-ray detector.}
	\label{fig:hist}
\end{figure}

@@

Let $N(x,y)$ be the grey value of the pixel at position $(x,y)$ in the obtained image. Similarly let $U(x,y)$ be they grey value of pixels of the shading free image. The shading effects can be modelled using a linear relationship
\begin{equation}
N(x,y) = U(x,y)b(x,y) + a(x,y)
\end{equation} 
where $b(x,y)$ is the multiplicative effect and $a(x,y)$ is the additive effect \cite{munzenmayer2003enhancing}. If it is possible to estimate the functions $b(x,y)$ and $a(x,y)$ using the estimators $\widehat{b}(x,y)$ and $\widehat{a}(x,y)$ respectively, then the shading-free image can be estimated using the estimator
\begin{equation}
\widehat{U}(x,y) = \frac{N(x,y)-\widehat{a}(x,y)}{\widehat{b}(x,y)} \times c_1 + c_2
\end{equation}
where $c_1$ and $c_2$ are user defined constants.
One method to estimate the images $b(x,y)$ and $a(x,y)$ is to use the black and white (b/w) images. Let $\overline{B}(x,y)$ and $\overline{W}(x,y)$ be the sample mean between the 20 black and white images respectively. The estimators for $b(x,y)$ and $a(x,y)$ are
\begin{equation}
\widehat{b}(x,y) = \overline{W}(x,y) - \overline{B}(x,y)
\end{equation}
and
\begin{equation}
\widehat{a}(x,y) = \overline{B}(x,y)
\end{equation}
respectively \cite{young2000shading}.

@@

Let $R_\text{b}(x,y)$, $R_\text{g}(x,y)$ and $R_\text{w}(x,y)$ be the grey value of the pixel, at position $(x,y)$, of the sample mean b/g/w images respectively. Let these images have $h$ rows and $w$ columns. The shading free b/g/w images should be completely flat, in other words all the pixels should have the same grey value. A good guess what that grey value should be would be the sample mean of the grey values within the b/g/w images $\overline{R}_\text{b}$, $\overline{R}_\text{g}$ and $\overline{R}_\text{w}$ where
\begin{equation}
\overline{R}_j=\frac{\sum_{x=1}^w\sum_{y=1}^hR_j(x,y)}{n}
\end{equation}
for $j\in\{\text{b},\text{g},\text{w}\}$. By treating these within image sample mean grey values as the true shading free grey value, then the problem becomes a linear regression with 3 data points.

@@

\begin{figure*}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/shadingCorrection/block.eps}
		\caption{Shading uncorrected}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/shadingCorrection/block_shadingCorrected.eps}
		\caption{b/g/w shading correction}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_shadingCorrection.eps}
		\caption{b/g/w 2nd order polynomial shading correction}
	\end{subfigure}
	\caption{A x-ray CT scan image before and after b/g/w shading correction.}
	\label{fig:shadingCorrection}
\end{figure*}

@@

To avoid dealing with dead pixels \cite{brettschneider2014spatial}, a method was considered which smoothed the reference images prior to any shading correction parameter estimation. The purpose of this was to iron out any misbehaving pixels in the reference images and to capture the shading effects parametrically. Second order panel-wise surface polynomials were fitted to the b/g/w images, this is shown in Figure \ref{fig:polynomial_shadingCorrection}. The standardised residuals from the panel-wise fit are shown in Figure \ref{fig:polynomial_residual}. A quick inspection of the residuals shows any characteristics not captured by the panel-wise fit. In the black and grey images, the residuals showe a global ring which was very unusual for the black image because it is detecting no x-rays at all. The b/g/w residuals all showed vertical stripes. The panel-wise fit can be improved by including a global polynomial fit to capture between panel effects. Higher order polynomials can be considered but overfitting may be possible, as a result of higher order polynomials attempting to capture all the characteristics of the b/g/w images.

@@

\begin{figure*}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_black.eps}
		\caption{Black}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_grey.eps}
		\caption{Grey}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_white.eps}
		\caption{White}
	\end{subfigure}
	\caption{Second order panel-wise surface polynomials fit on the reference images.}
	\label{fig:polynomial_shadingCorrection}
\end{figure*}

@@

Table \ref{table:bgw_anova} shows the within and between pixel variance of the grey values. The table shown that b/w and b/g/w shading correction does make an improvement because it brings the within and between pixel variances closer together. The performance of shading correction on the black and grey images appeared to depend if the grey images were used in training the shading correction. The b/g/w 2nd order polynomial shading correction does perform by bringing the within and between pixel variances closer together but not as much as b/w and b/g/w shading correction.

@@

In conclusion, b/w and b/g/w shading correction do perform well because there was evidence they are attempting to iron out all the pixel grey values to have the same mean. The b/g/w 2nd order polynomial shading correction does its job. However because the panel wise polynomial under fitted and did not capture all the shading effects, the shading correction also did not capture all the shading effects.

@@

The object of interest is the 3D printed sample. In the mini-project, it was found the background and the foam holding the 3D printed sample have different mean variance relationships \cite{ip2016inside}. Thus to model the mean variance relationship of the 3D printed sample, the 3D printed sample was segmented from the background and the foam. This was done by cropping the scans of the 3D printed sample in half, removing the bottom half containing the foam. Next a threshold was conducted using the following procedure: 
\begin{itemize}
	\item For each of the 20 b/g/w images, apply a panel wise median filter of size $3\times3$. Pixels outside the panels were symmetrically extended.
	\item Use these filtered reference images for shading correction.
	\item Take the mean over all shading corrected scans.
	\item Keep pixels with grey values less than $4.7\times 10^4$.
\end{itemize}
This method of segmentation was developed by informal experimentation. The resulting segmented image is shown in Figure \ref{fig:segment}. Other segmentation methods could be considered but further study of other methods may not be necessary here.

\begin{figure}
	\centering
	\includegraphics[width = 0.45 \textwidth]{../figures/meanVar/segment.eps}
	\caption{Resulting segmentation of the 3D printed sample}
	\label{fig:segment}
\end{figure}

@@

GLM can model the sample variance as the response variable being Gamma distributed, explained by the sample mean through a link function $g(\text{variance})$. Fitting of the model was done using iterative re-weighted least squares. The dispersion parameter need not to be estimated because the shape parameter is known. A linear fit using the identity link did show that the Gamma response captured the spread of the sample variance for different sample means, this is shown in Figure \ref{fig:meanVar_sampleSize}.

\begin{figure*}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_25.eps}
		\caption{$n=25$}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_50.eps}
		\caption{$n=50$}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_75.eps}
		\caption{$n=75$}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_100.eps}
		\caption{$n=100$}
	\end{subfigure}
	\caption{Mean and variance frequency density plot of each pixel's grey value in the segmented image of the 3D printed sample. The sample variance and sample mean were estimated using $n$ scans selected at random without replacement. A Gamma GLM was fitted with the identity link. The solid and dotted lines are the mean response and the $\Phi(\pm 1)$ quantiles respectively.}
	\label{fig:meanVar_sampleSize}
\end{figure*}

@@

\begin{figure*}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_identity.eps}
		\caption{Identity link, order 1}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_log.eps}
		\caption{Log link, order -1}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_canonical_1.eps}
		\caption{Inverse link, order -1}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_canonical_2.eps}
		\caption{Inverse link, order -2}
	\end{subfigure}
	\caption{Shading uncorrected mean and variance frequency density plot of each pixel's grey value in the segmented image of the 3D printed sample. A Gamma GLM was fitted with different link functions and polynomial order. The solid and dotted lines are the mean response and the $\Phi(\pm 1)$ quantiles respectively.}
	\label{fig:meanVar_link}
\end{figure*}

@@

\begin{figure*}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_no_shad.eps}
		\caption{No shading correction}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_bw.eps}
		\caption{b/w shading correction}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_bgw.eps}
		\caption{b/g/w shading correction}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_polynomial.eps}
		\caption{b/g/w 2nd order polynomial shading correction}
	\end{subfigure}
	\caption{Post shading correction mean and variance frequency density plot of each pixel's grey value in the segmented image of the 3D printed sample. A Gamma GLM was fitted with the identity link. The solid and dotted lines are the mean response and the $\Phi(\pm 1)$ quantiles respectively.}
	\label{fig:meanVar_shadingCorrection}
\end{figure*}

@@

For a given link function, polynomial order and shading correction, the 100 images of the 3D printed sample were spilt into two equally sized sets: the training set and the test set. The within pixel sample mean and sample variance  grey value was estimated for both the training set and test set separately. The GLM was fitted onto the mean variance data obtained from the training set. The fitted model was then used to predict the variance given the mean on the test set. The predicted variance given the mean then can be compared with the sample variance.

Metrics such as the mean squared error can be used to assess how good the prediction is. However it should be noted that there is sampling error in the sample variance and the magnitude of the error varies for different means. In order to take the varying sampling error into account, the mean standardised squared error (MSSE) was used to assess the performance of the fitted GLM predicting the variance given the mean. The errors were standardised by dividing by the standard deviation of the GLM response.

@@

\begin{figure*}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/residual_no_shad.eps}
		\caption{No shading correction}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/residual_bw.eps}
		\caption{b/w shading correction}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/residual_bgw.eps}
		\caption{b/g/w shading correction}
	\end{subfigure}
	\caption{Frequency density plot of the standardised residuals from predicting the variance given the mean of the test test using a training GLM with identity link function.}
	\label{fig:glm_residual}
\end{figure*}

In conclusion it was found that b/g/w shading correction aid in variance prediction by making the mean variance data more linear. A simple identity link perform just as well as other link function which suggests a linear relationship between the variance and the mean.

@@

A statistic was developed which compares each pixel of a scan of a 3D printed sample with the true image obtained from a computer model or simulation. Any outlying pixels then can be considered as a possible defect in the 3D printed sample. The statistic is based on the $Z$ statistic and is given as
\begin{equation}
Z(x,y) = \frac{\text{scan}(x,y) - \text{model}(x,y)}{\sqrt{\widehat{\variance}[\text{scan}(x,y)]}}
\end{equation}
%$Z(x,y)=\frac{\text{scan}(x,y)-\text{model}(x,y)}{\sqrt{\widehat{\mathbb{V}\text{ar}}[\text{scan}(x,y)]}}$
where $\widehat{\variance}[\text{scan}(x,y)]$ is the estimated grey value variance of a pixel at $(x,y)$ of the scan. The estimated variance can be obtained using a GLM model as discussed in the previous section. In addition, the scan image should be shaded corrected to remove as much shading effects as possible. Assuming the $Z$ statistics are standard Normal distributed, multiple hypothesis testing can be used to test each pixel to find significant or outlying pixels, such as the Bonferroni correction.

\subsection{Experiments}
An experiment was conducted to investigate the behaviour of the $Z$ statistics. b/g/w shading correction was applied prior to the experiment and any outlying pixels were interpolated as discussed in the previous section. The 100 images were spilt into 3 parts:
\begin{itemize}
	\item 50 images in the training set to train the mean variance relationship model using GLM with the identity link;
	\item 25 images in the truth set, the mean over these images were used as the true image;
	\item 25 images in the test set, each of these images will be compared to the true image.
\end{itemize}
Each image in the test set was compared to the true image by calculating the $Z$ statistic for each pixel. Thus for each pixel, a sample of 25 $Z$ statistics was obtained.

A sample of $Z$ images are shown in Figure \ref{fig:p_values} and significant pixels are shown in Figure \ref{fig:critical_values}. The Bonferroni correction was used to correct for multiple testing. The $Z$ images showed that the $Z$ statistics within image varied scan to scan, suggesting images in the test set are not quite as similar as hoped for. Common significant pixels were picked up by the statistic, especially on the left edge. Fortunately only a few significant pixels were picked up from the 3D printed sample.

\begin{figure}
	\centering
	\includegraphics[width = 0.45\textwidth]{../figures/meanVar/p_values.eps}
	\caption{A sample of 6 images from the test set compared to the true image. The $Z$ statistics were transformed using the standard Normal c.d.f.}
	\label{fig:p_values}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width = 0.45\textwidth]{../figures/meanVar/critical_values.eps}
	\caption{Using the $Z$ statistics from Figure \ref{fig:p_values}, highlighted in red are significant pixels at the $5\sigma$ significance level corrected for multiple tests using the Bonferroni correction.}
	\label{fig:critical_values}
\end{figure}

The $Z$ statistics were tested for Normality within pixel using the $\chi^2$ goodness of fit test. To make the test more powerful, 75 more $Z$ statistics were collected by reassigning the training, truth and test set and repeating the experiment 3 more times. Figure \ref{fig:chi_squared} show the $p$ values from the test were particularly low, especially on the bottom half of the image. In particular there is a vertical line of significant pixels as well. Normality may be a valid assumption but the bottom of the image where the foam is may break such an assumption.

\begin{figure*}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width = \textwidth]{../figures/meanVar/chi_squared_critical.eps}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width = \textwidth]{../figures/meanVar/chi_squared_p_values.eps}
	\end{subfigure}
	\caption{$p$ values from the $\chi^2$ goodness of fit test within pixel. Highlighted in red are significant pixels at the $2\sigma$ significant level corrected for multiply testing using the Bonferroni correction.}
	\label{fig:chi_squared}
\end{figure*}

>>>>

\section{About the Data}
Data was collected prior to the mini-project. 20 black/grey/white (b/g/w) images were collected on 14/03/16 at around 1250. The b/g/w images are images obtained from the x-ray detector when exposed to x-rays at different settings. They are useful for calibrating the detector, thus b/g/w images can be called reference images. About 2 hours later, 100 images of a 3D printed cuboid (or sample) were taken. These images were obtained from the x-ray detector when exposed to x-rays with the sample between the x-ray source and detector. The 3D printed sample was stationary and not rotating throughout the scans. The sample was held at the bottom by foam. The detector used was the Perkin Elmer XRD 1621 digital x-ray detector, with settings shown in Table \ref{table:settings}.

@@

The images were $(1\,996\times1\,996)$ pixels in size and are in greyscale with 16 bits, in other words each pixel can have grey values which take integer values from 0 to $2^{16}-1$ inclusive. The grey values are in arbitrary units. A sample of images are shown in Figure \ref{fig:image} and the histogram of grey values are shown in Figure \ref{fig:hist}.

\begin{figure*}
	\centering
	\includegraphics[width = \textwidth]{../figures/data/140316_image.png}
	\caption{A black, grey, white and sample image obtained from the x-ray detector.}
	\label{fig:image}
\end{figure*}

\begin{figure}
	\centering
	\includegraphics[width = 0.45\textwidth]{../figures/data/140316_histo.eps}
	\caption{Histogram of grey values from a black, grey, white and sample image obtained from the x-ray detector.}
	\label{fig:hist}
\end{figure}

@@

Let $N(x,y)$ be the grey value of the pixel at position $(x,y)$ in the obtained image. Similarly let $U(x,y)$ be they grey value of pixels of the shading free image. The shading effects can be modelled using a linear relationship
\begin{equation}
N(x,y) = U(x,y)b(x,y) + a(x,y)
\end{equation} 
where $b(x,y)$ is the multiplicative effect and $a(x,y)$ is the additive effect \cite{munzenmayer2003enhancing}. If it is possible to estimate the functions $b(x,y)$ and $a(x,y)$ using the estimators $\widehat{b}(x,y)$ and $\widehat{a}(x,y)$ respectively, then the shading-free image can be estimated using the estimator
\begin{equation}
\widehat{U}(x,y) = \frac{N(x,y)-\widehat{a}(x,y)}{\widehat{b}(x,y)} \times c_1 + c_2
\end{equation}
where $c_1$ and $c_2$ are user defined constants.
One method to estimate the images $b(x,y)$ and $a(x,y)$ is to use the black and white (b/w) images. Let $\overline{B}(x,y)$ and $\overline{W}(x,y)$ be the sample mean over the 20 black and white images respectively. The estimators for $b(x,y)$ and $a(x,y)$ are
\begin{equation}
\widehat{b}(x,y) = \overline{W}(x,y) - \overline{B}(x,y)
\end{equation}
and
\begin{equation}
\widehat{a}(x,y) = \overline{B}(x,y)
\end{equation}
respectively \cite{young2000shading}.

@@

Let $R_\text{b}(x,y)$, $R_\text{g}(x,y)$ and $R_\text{w}(x,y)$ be the grey value of the pixel, at position $(x,y)$, of the sample mean b/g/w images respectively. Let these images have $h$ rows and $w$ columns. The shading free b/g/w images should be completely flat, in other words all the pixels within a reference image should have the same grey value. A good guess what that shading corrected grey value should be would be the sample mean of the shading uncorrected grey values within the b/g/w images $\overline{R}_\text{b}$, $\overline{R}_\text{g}$ and $\overline{R}_\text{w}$ where
\begin{equation}
\overline{R}_j=\frac{\sum_{x=1}^w\sum_{y=1}^hR_j(x,y)}{n}
\end{equation}
for $j\in\{\text{b},\text{g},\text{w}\}$. By treating these within image sample mean grey values as the true shading free grey value, then the problem becomes a linear regression with 3 data points.

@@

\begin{figure*}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/shadingCorrection/block.png}
		\caption{Shading uncorrected}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/shadingCorrection/block_shadingCorrected.png}
		\caption{b/g/w shading correction}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_shadingCorrection.png}
		\caption{b/g/w 2nd order polynomial shading correction}
	\end{subfigure}
	\caption{A x-ray CT scan image before and after b/g/w shading correction.}
	\label{fig:shadingCorrection}
\end{figure*}

@@

To avoid dealing with dead pixels \cite{brettschneider2014spatial}, a method was considered which smoothed the reference images prior to any shading correction parameter estimation. The purpose of this was to iron out any misbehaving pixels in the reference images and to capture the shading effects parametrically. Second order panel-wise surface polynomials were fitted to the b/g/w images, this is shown in Figure \ref{fig:polynomial_shadingCorrection}. The standardised residuals from the panel-wise fit are shown in Figure \ref{fig:polynomial_residual}. A quick inspection of the residuals shows any characteristics not captured by the panel-wise fit. In the black and grey images, the residuals showed a global ring which was very unusual for the black image because it is detecting no x-rays at all. The b/g/w residuals all showed vertical stripes. The panel-wise fit can be improved by including a global polynomial fit to capture between panel effects. Higher order polynomials can be considered but overfitting may be possible as may attempt to capture all the characteristics of the b/g/w images.

@@

\begin{figure*}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_black.png}
		\caption{Black}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_grey.png}
		\caption{Grey}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_white.png}
		\caption{White}
	\end{subfigure}
	\caption{Second order panel-wise surface polynomials fit on the reference images.}
	\label{fig:polynomial_shadingCorrection}
\end{figure*}

@@

Table \ref{table:bgw_anova} shows the within and between pixel variance of the grey values. The table shown that b/w and b/g/w shading correction does make an improvement because it brings the within and between pixel variances closer together. The performance of shading correction on the black and grey images appeared to depend on if the grey images were used in training the shading correction. The b/g/w 2nd order polynomial shading correction does perform by bringing the within and between pixel variances closer together but not as much as b/w and b/g/w shading correction.

@@

In conclusion, b/w and b/g/w shading correction did perform well because there was evidence they are attempting to iron out all the pixel grey values to have the same mean. The b/g/w 2nd order polynomial shading correction does its job. However because the panel wise polynomial under fitted and did not capture all the shading effects, the shading correction also did not capture all the shading effects.

@@

In the mini-project, it was found the background and the foam holding the 3D printed sample have different mean variance relationships \cite{ip2016inside}. The object of interest is the 3D printed sample. Thus to model the mean variance relationship of the 3D printed sample, the 3D printed sample was segmented from the background and the foam. This was done by cropping the scans of the 3D printed sample in half, removing the bottom half containing the foam. Next a threshold was conducted using the following procedure: 
\begin{itemize}
	\item For each of the 20 b/g/w images, apply a panel wise median filter of size $3\times3$. Pixels outside the panels were symmetrically extended.
	\item Use these filtered reference images for shading correction.
	\item Take the mean over all 100 shading corrected scans.
	\item Keep pixels with grey values less than $4.7\times 10^4$.
\end{itemize}
This method of segmentation was developed by informal experimentation. The resulting segmented image is shown in Figure \ref{fig:segment}. Other segmentation methods could be considered but further study of other methods may not be necessary here.

\begin{figure}
	\centering
	\centerline{
	\includegraphics[width = 0.5 \textwidth]{../figures/meanVar/segment.png}
	}
	\caption{Resulting segmentation of the 3D printed sample}
	\label{fig:segment}
\end{figure}

@@

GLM can model the sample variance as a Gamma distributed response variable, being explained by the sample mean through a link function $g(\text{variance})$. Fitting of the model was done using iterative re-weighted least squares. The dispersion parameter need not to be estimated because the shape parameter $(n-1)/2$ is known. A linear fit using the identity link did show that the Gamma response captured the spread of the sample variance for different sample means, this is shown in Figure \ref{fig:meanVar_sampleSize}.

\begin{figure*}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_25.png}
		\caption{$n=25$}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_50.png}
		\caption{$n=50$}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_75.png}
		\caption{$n=75$}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_100.png}
		\caption{$n=100$}
	\end{subfigure}
	\caption{Within pixel mean and variance grey value frequency density plot of each pixel in the segmented image of the 3D printed sample. The sample variance and sample mean were estimated using $n$ scans selected at random without replacement. A Gamma GLM was fitted with the identity link. The solid and dotted lines are the mean response and the $\Phi(\pm 1)$ quantiles respectively.}
	\label{fig:meanVar_sampleSize}
\end{figure*}

@@

\begin{figure*}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_identity.png}
		\caption{Identity link, order 1}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_log.png}
		\caption{Log link, order -1}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_canonical_1.png}
		\caption{Inverse link, order -1}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_canonical_2.png}
		\caption{Inverse link, order -2}
	\end{subfigure}
	\caption{Shading uncorrected within pixel mean and variance grey value frequency density plot of each pixel in the segmented image of the 3D printed sample. A Gamma GLM was fitted with different link functions and polynomial ordera. The solid and dotted lines are the mean response and the $\Phi(\pm 1)$ quantiles respectively.}
	\label{fig:meanVar_link}
\end{figure*}

@@

\begin{figure*}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_no_shad.png}
		\caption{No shading correction}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_bw.png}
		\caption{b/w shading correction}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_bgw.png}
		\caption{b/g/w shading correction}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_polynomial.png}
		\caption{b/g/w 2nd order polynomial shading correction}
	\end{subfigure}
	\caption{Post shading correction within pixel mean and variance grey value frequency density plot of each pixel in the segmented image of the 3D printed sample. A Gamma GLM was fitted with the identity link. The solid and dotted lines are the mean response and the $\Phi(\pm 1)$ quantiles respectively.}
	\label{fig:meanVar_shadingCorrection}
\end{figure*}

@@

For a given link function, polynomial order and shading correction, the 100 images of the 3D printed sample were spilt into two equally sized sets: the training set and the test set. The within pixel sample mean and sample variance grey value were estimated for both the training set and test set separately. The GLM was fitted onto the mean variance data obtained from the training set. The fitted model was then used to predict the variance given the mean. The predicted variance given the mean then can be compared with the sample variance.

There is sampling error in the sample variance and the magnitude of the error varies for different means. In order to take the varying sampling error into account, the mean standardised squared error (MSSE) was used to assess the performance of the fitted GLM predicting the variance given the mean. The errors were standardised by dividing by the standard deviation of the GLM response.

@@

\begin{figure*}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/residual_no_shad.png}
		\caption{No shading correction}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/residual_bw.png}
		\caption{b/w shading correction}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/meanVar/residual_bgw.png}
		\caption{b/g/w shading correction}
	\end{subfigure}
	\caption{Frequency density plot of the standardised residuals from predicting the variance given the mean in test set using a training GLM with identity link function.}
	\label{fig:glm_residual}
\end{figure*}

In conclusion it was found that b/g/w shading correction aid in variance prediction by making the mean variance data more linear. A simple identity link performed just as well as other link functions which suggests a linear relationship between the variance and the mean could be sufficient enough for the purpose of variance prediction.

@@

A statistic was developed which compares each pixel of a single scan of a 3D printed sample with the true image obtained from a computer model or simulation. Any outlying pixels then can be considered as a possible defect in the 3D printed sample. The statistic is based on the $Z$ statistic and is given as
\begin{equation}
Z(x,y) = \frac{\text{scan}(x,y) - \text{model}(x,y)}{\sqrt{\widehat{\variance}[\text{scan}(x,y)]}}
\end{equation}
%$Z(x,y)=\frac{\text{scan}(x,y)-\text{model}(x,y)}{\sqrt{\widehat{\mathbb{V}\text{ar}}[\text{scan}(x,y)]}}$
where $\widehat{\variance}[\text{scan}(x,y)]$ is the estimated grey value variance of a pixel at $(x,y)$ of the scan. The estimated variance can be obtained using a GLM model as discussed in the previous section. In addition, the scan image should be shading corrected to remove as much shading effects as possible. Assuming the $Z$ statistics are standard Normal distributed, multiple hypothesis testing can be used to test each pixel to find significant or outlying pixels, such as the Bonferroni correction.

\subsection{Experiments}
An experiment was conducted to investigate the behaviour of the $Z$ statistics. b/g/w shading correction was applied prior to the experiment and any outlying pixels were interpolated as discussed in the previous section. The 100 images were spilt into 3 parts:
\begin{itemize}
	\item 50 images in the training set to train the mean variance relationship model using GLM, as described in the previous section, with the identity link;
	\item 25 images in the truth set, the mean over these images were used as the true image;
	\item 25 images in the test set, each of these images will be compared to the true image.
\end{itemize}
Each image in the test set was compared to the true image by calculating the $Z$ statistic for each pixel. Thus for each pixel, a sample of 25 $Z$ statistics was obtained.

A sample of $Z$ statistics are shown in Figure \ref{fig:p_values} and significant pixels are shown in Figure \ref{fig:critical_values}. The Bonferroni correction was used to correct for multiple testing. The $Z$ statistics within image varied scan to scan, suggesting images in the test set were not quite as similar to each other as hoped for. Common significant pixels were picked up by the statistic, especially on the left edge. Fortunately only a few significant pixels were picked up from the 3D printed sample, implying only a few false positives were detected.

\begin{figure}
	\centering
	\centerline{
	\includegraphics[width = 0.5\textwidth]{../figures/meanVar/p_values.png}
	}
	\caption{A sample of $Z$ statistics obtained from comparing a scan from the test set to the true image. The $Z$ statistics were transformed using the standard Normal c.d.f.}
	\label{fig:p_values}
\end{figure}

\begin{figure}
	\centering
	\centerline{
	\includegraphics[width = 0.5\textwidth]{../figures/meanVar/critical_values.png}
	}
	\caption{Using the $Z$ statistics from Figure \ref{fig:p_values}, highlighted in red are significant pixels at the $5\sigma$ significance level corrected for multiple tests using the Bonferroni correction.}
	\label{fig:critical_values}
\end{figure}

The $Z$ statistics within pixel were tested for Normality  using the $\chi^2$ goodness of fit test. To make the test more powerful, 75 more $Z$ statistics were collected by reassigning randomly the training, truth and test set and repeating the experiment 3 more times. Figure \ref{fig:chi_squared} showed that the $p$ values from the $\chi^2$ test were particularly low, especially on the bottom half of the image. In particular there is a vertical line of significant pixels as well. Normality may be a valid assumption but the bottom of the image where the foam is may break such an assumption.

\begin{figure*}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width = \textwidth]{../figures/meanVar/chi_squared_critical.png}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width = \textwidth]{../figures/meanVar/chi_squared_p_values.eps}
	\end{subfigure}
	\caption{$p$ values from the $\chi^2$ goodness of fit test within pixel. Highlighted in red are significant pixels at the $2\sigma$ significant level corrected for multiply testing using the Bonferroni correction.}
	\label{fig:chi_squared}
\end{figure*}

\subsection{Conclusion}
The $Z$ statistics looked like a good candidate to make inference from a single scan of a 3D printed sample. There is further work to be done. Rather than using a subset of the data as the true image, simulations can be treated as the true image to investigate how well the $Z$ statistic perform in real life defect detection. Further multiple hypothesis testing should be investigated and inference can be extended to the 3D reconstructed data of the 3D printed sample.
